\documentclass[conference]{IEEEtran}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{ebgaramond-maths}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
    
\begin{document}

\title{Enron Email Fraud Analysis* \\
{\footnotesize \textsuperscript{*}Comp 550 - Fall 2023 semester group project}
}

\author{\IEEEauthorblockN{David Hobson}
\IEEEauthorblockA{\textit{dept. of Computer Science} \\
\textit{McGill Univerity}\\
Montreal, Canada \\
david.hobson@mail.mcgill.ca}
\and
\IEEEauthorblockN{Caleb Moses}
\IEEEauthorblockA{\textit{dept. of Computer Science} \\
\textit{McGill Univerity}\\
Montreal, Canada \\
caleb.moses@mail.mcgill.ca}
\and
\IEEEauthorblockN{Svetla Vassileva}
\IEEEauthorblockA{\textit{dept. of Computer Science} \\
\textit{McGill Univerity}\\
Montreal, Canada \\
svetla.vassileva@mail.mcgill.ca}
}
\maketitle

\begin{abstract}
A short overview of the paper.
\end{abstract}

\section{Introduction}
What is the motivation behind the project? In general terms, what is the hypothesis that you test and how do you go about doing so?

\section{Related Work}
Summarize previous work in the area that you have found. I don't expect you to give a complete and fully up-to-date survey of related work in the area. Instead, aim to cite and discuss at least 3-5 relevant papers, with a focus on how your work differs from theirs.

\section{Method}
Describe the model that you implement, the data set that you use, and any other materials. There should be sufficient details that another researcher is able to more or less replicate your experiment with some effort.

\section{Results}
Report the results of your experiment, and any general trends that you see. If the evaluation measure used is not a standard one, be sure to define that as well.

\section{Discussion and Conclusion}
What conclusions can be drawn from your experiments? Was your initial hypothesis verified? What are the limitations of your work, and how could it be extended?

\section{Statement of Contributions}
Briefly describe each member's contribution. All project members are expected to contribute to the project. While each member may perform different tasks, you should strive for an equal distribution of work. In particular, all members of the project should participate in the design of the project, be involved in writing, and be involved in the implementation in some way.

\end{document}
